Exploring the Usefulness of Varactor loaded Nonlinear Transmission Lines

### 2020-06-02 RohdeAndSchwarzWhitePaper/Draft_White_Paper.tex
Made some report edits

@@

>>>>

Figure \ref{fig:ACResp56nh} shows the simulated AC response of our 10 ladder long circuit.

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth,page = 1]{ACResponseB1.png}
\caption{\ AC Response of Board 1 (L = 56nH) 
}\label{fig:ACResp56nh}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth,page = {1}]{Probed_Input_N10_N240_NoSeriesResistance.pdf}
\caption{\ Risetime Vs. Line Length vs. DC Bias Voltage 
}\label{fig:ProbedNoSeriesR}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth,page = {1}]{Probed_Input_N10_N240_With_SeriesResistance.pdf}
\caption{\ Risetime Vs. Line Length vs. DC Bias Voltage 
}\label{fig:ProbedSeriesR}
\end{figure}
